Highly Available Transactions: Virtues and Limitations

### 2013-03-31 writeup/evaluation.tex

\vspace{.5em}\noindent\textbf{Commutativity and Monotonicity} Recent
work on the CALM Theorem~\cite{calm}, Lattice-based state
update~\cite{blooml}, and Commutative and Replicated Data
Types~\cite{crdt} demonstrates that, if updates logically commute,
then they can often be safely performed in different orders at
different replicas. Accordingly, as long as all writes are delivered
to all replicas, then a system executing monotonic logic with
commutative operators may not suffer from application-level
consistency anomalies as a result of Lost Update or Write Skew
anomalies. However, applications with non-monotonic state mutation
will not, in general, be able to maintain application-level
consistency constraints with HATs alone. Moreover, applications with
requiring bounded update visibility latency should opt for
unavailability.

>>>>

\vspace{.5em}\noindent\textbf{Commutativity and Monotonicity} Recent
work on the CALM Theorem~\cite{calm} and Commutative and Replicated Data
Types~\cite{crdt} demonstrates that, if updates logically commute,
then they can often be safely performed in different orders at
different replicas. Accordingly, as long as all writes are delivered
to all replicas, then a system executing monotonic logic with
commutative operators may not suffer from application-level
consistency anomalies as a result of Lost Update or Write Skew
anomalies. However, applications with non-monotonic state mutation
will not, in general, be able to maintain application-level
consistency constraints with HATs alone. Moreover, applications with
requiring bounded update visibility latency should opt for
unavailability.
